---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgsite

<!-- badges: start -->
<!-- badges: end -->

The goal of `pkgsite` is to make it easier to create a package website using
Quarto. It attempts to do for R what 
[Quartodoc](https://machow.github.io/quartodoc/get-started/overview.html) does 
for Python package documentation. 

### When should I use `pkgsite`?

In the vast majority of cases, [`pkgdown`](https://pkgdown.r-lib.org/index.html)
is enough to create a well refined package website. `pkgdown` is a well developed
mature package that covers all sorts of special needs. In fact, `pkgsite` 
actually uses `pkgdown` to perform several operations.

So apart for wanting a Quarto site for your R package, a couple of reasons to 
use `pkgsite` to create your reference Quarto pages are:

- **You want to use the output 
["freeze"](https://quarto.org/docs/projects/code-execution.html#freeze) 
capabilities in Quarto** - You would like  the examples in the help pages to
run, but, the ability to run such examples depend on specific technologies
to be accessible to where the site is being 
published, which is usually GitHub. Examples of those technologies could be
databases, Spark and Large Language Models. The idea would be to render the
website locally, where you would have access to the needed technologies, and
make commit the resulting "_freeze" folder to the repository. This will allow
any re-building of your website by GitHub to have the necessary code output to
create the HTML files.

- **You want to build a unified site** - Your packages from your project may be
available in multiple languages, and wish to make a unified website. The idea
here is if you have output from Quartodoc from the Python side of your project,
that needs to be available in the website along with the references from the
R side of your project. 

An example of having both reasons to use `pkgsite`, is the 
[`mall`](https://github.com/mlverse/mall) package. This project has a Python, and
an R package. And the examples in both packages need an LLM in order to work, 
here is the resulting [reference pages](https://mlverse.github.io/mall/reference/).

## Installation

You can install the development version of pkgsite from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgararuiz/pkgsite")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(pkgsite)

write_reference()
```
